Psyc 601 Multivariate Statistics Project

### 2013-08-26 writeups/proposal/proposal.tex
foo
Former-commit-id: bbe158597345a1535a7222e188fbdaa106db5e2f [formerly 6124dcd79c54c56ada68c48530b604c1446701ea]
Former-commit-id: c00831fb6c30ad4867601c8d3a7d7e39001bd166

\textcite{Kywe2012} also customized their tag predictino model to the user's past hashtag use, and was one of the first to do so when developing a hashtag-prediction model for Twitter.
The set of recommended hashtags was the union of hashtags used in similar tweets and hashtags used by similar users.
This was done by storing a content vector of hshtag use for each user (user-centered approach) alongside the content vectors of hashtag use for each tweet (tweet-centered approach).
To generate recommended hashtags, the model would return the top-ranked hashtags from the hashtags used in 0-50 similar tweets and 0-4 similar users.
Prediction accuracy improved when the model generated recommendations based on hashtags in both similar tweets and the top few similar users compared to basing recommendations on similar tweets alone.

>>>>

\textcite{Kywe2012} also customized their tag predictino model to the user's past hashtag use, and was one of the first to do so when developing a hashtag-prediction model for Twitter.
The set of recommended hashtags was the union of hashtags used in similar tweets and hashtags used by similar users.
This was done by storing a content vector of hshtag use for each user (user-centered approach) alongside the content vectors of hashtag use for each tweet (tweet-centered approach).
To generate recommended hashtags, the model would return the top-ranked hashtags from the hashtags used in 0-50 similar tweets and 0-4 similar users.
Prediction accuracy improved when the model combined recommendations based on hashtags in both similar tweets and the top few similar users compared to basing recommendations on similar tweets alone.
